---
title: "Audit report"
subtitle: "Reproducibility and traceability record"
author: "DIPEL-IMARPE"
date: today
format:
  html:
    toc: true
    code-fold: true
  docx:
    toc: true
execute:
  warning: false
  message: false
---

# Objective

This audit document records the main elements needed to trace and reproduce the analysis.

# Repository information

```{r}
#| label: git-info
get_git_value <- function(args) {
  tryCatch(system2("git", args, stdout = TRUE, stderr = TRUE)[1], error = function(e) NA_character_)
}

tibble::tibble(
  field = c("git_commit", "git_branch", "repository_status"),
  value = c(
    get_git_value(c("rev-parse", "HEAD")),
    get_git_value(c("rev-parse", "--abbrev-ref", "HEAD")),
    get_git_value(c("status", "--short"))
  )
)
```

# Data sources

```{r}
#| label: data-sources
if (file.exists("metadata/data_sources.yml")) {
  yaml::read_yaml("metadata/data_sources.yml")
} else {
  "metadata/data_sources.yml not found"
}
```

# Checksums

```{r}
#| label: checksums
if (file.exists("metadata/checksums.csv")) {
  readr::read_csv("metadata/checksums.csv", show_col_types = FALSE)
} else {
  "metadata/checksums.csv not found"
}
```

# Pipeline status

```{r}
#| label: target-status
if (requireNamespace("targets", quietly = TRUE)) {
  targets::tar_meta(fields = c(name, command, time, bytes, format, repository))
} else {
  "targets package not installed"
}
```

# R session

```{r}
#| label: session-info
sessionInfo()
```

# Reproducibility checklist

| Item | Status | Notes |
|---|---|---|
| Data sources documented | pending | See `metadata/data_sources.yml` |
| Required columns documented | pending | See `metadata/schema.yml` |
| Pipeline executed | pending | Run `targets::tar_make()` |
| Report rendered | pending | Run `quarto render index.qmd` |
| Audit rendered | pending | Run `quarto render audit.qmd` |
| Release created | pending | Create a tag/release for official output |
